---
title: "IP Lookup"
author: "Barry Bullas"
date: "16/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- c("rvest", "dplyr", "httr", "xml2", "jsonlite", "DT", "here", "readtext", "data.table")

new_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages, repos = "https://cloud.r-project.org/")

#Load required packages
lapply(list_of_packages, library, character.only = TRUE)

#Load fields from csv to display
fields <- read.csv(here("data/fields.csv"))
```

## IPAPI
In this project we will use the [IPAPI](https://ipapi.co/) to lookup information about IP addresses.

The API allows you to look up information on IP addressess.  Under the free tier, you get up-to 1000 IP lookups in a day (approximately 30K/month). If you need more than this, they have a range of [pricing plans](https://ipapi.co/#pricing).

The key fields returned by the API are:
```{r echo=FALSE}
datatable(fields, rownames = FALSE)
```

# Return all information for an IP address

```{r}
# A random ip address to use
ip <- '185.86.151.11'

# URL 
url <- paste0('https://ipapi.co/', ip, '/json/')

# Get the reponse
get_response <- GET(url)

#Check status of response (200 is success)
status_code(get_response)

# Check http_type() of the response
http_type(get_response)

# Parse returned text with fromJSON()
search_content <- fromJSON(content(get_response, as = "text",  encoding = "UTF-8"), simplifyDataFrame = TRUE)

str(search_content)
```

# Return a specific field
By adding the field name to the url in place of the \json format we can return the specific field for an ip address in text format.  In this example we will return the Country Name for the IP address.

```{r}
# To return a specific field we add the field name to the url
# In this example we will return the country name
url <- paste0('https://ipapi.co/', ip, '/country_name')

# Get the response
get_field_response <- GET(url)

#Check status of response (200 is success)
status_code(get_field_response)

# Check http_type() of the response
http_type(get_field_response)

#list the headers
#headers(get_field_response)

# Get the field from the content
ips_country <- content(get_field_response)

```

# Result
The Country for `r ip` is `r ips_country`.